Recruiting Chapter

### 2021-06-11 text/manuscript_june_2021.Rmd
draft changes

This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities. We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3: to what extent do public research universities and private universities visit overlapping sets of private high schools? This research question is addressed, simultaneously, through the use of network graphs and by allocating each college/university to a "community" cluster.

@@

text

@@

text

@@

@@

@@

>>>>

This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities. We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3: to what extent do public research universities and private universities visit overlapping sets of private high schools?

We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks. First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph. In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.

@@

Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools. Table \@ref(tab:pubu-count-matrix) shows, for each pair of public universities (e.g., University of Alabama and University of South Caroline,  the number of high schools that were visited by both universities. For example, column 1 shows that of the X different private high schools visited by the University of Alabama, the University of California also visited X of these high schools. Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count. For example, of the X private high schools visited by CU Boulder, the University of Alabama visited X% of these high schools and the University of South Carolina visited X% of these high schools.

INSERT TABLE \@ref(tab:pubu-count-matrix) AND TABLE \@ref(tab:pubu-percent-matrix) ABOUT HERE

ADD PARAGRAPH THAT SUBSTANTIVELY INTERPRETS BIG PICTURE FINDINGS FROM THESE TABLES.

```{r, eval = FALSE, include = FALSE}
table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
table_1mode_pubu %>% glimpse()
```

DESCRIBE HOW TO READ TABLE AND WHAT THE RESULTS SHOW

INSERT TABLE X ABOUT HERE

Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network. Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices. In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a dotted line -- if both universities visit at least one high school in common.

For our one-mode public

We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks. First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph. In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.

INSERT FIGURE \@ref(fig:plot-1mode-pubu) ABOUT HERE

@@

INSERT TABLE \@ref(tab:privu-percent-matrix) ABOUT HERE

INSERT FIGURE \@ref(fig:plot-1mode-privu) ABOUT HERE

@@

INSERT FIGURE \@ref(fig:plot-1mode-u-k5) ABOUT HERE

@@

\clearpage

@@

\clearpage

```{r pubu-count-matrix}
table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))

kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 15), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(14, 16), width = '6em')
```

```{r pubu-percent-matrix}
kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(c(1, 15), width = '8.5em') %>% 
  column_spec(2:13, width = '7em') %>% 
  column_spec(c(14, 16), width = '6em')

```

\clearpage

```{r privu-count-matrix, eval=FALSE, include=FALSE}

table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))

kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')
```

```{r privu-percent-matrix}

table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))

kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em')

```
